PyQBench: a Python library for benchmarking gate-based quantum computers

### 2022-12-21 txt/manuscript.tex
ack

\section*{Required Metadata}
\label{}

@@

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this 
column} \\
\hline
C1 & Current code version & 0.1.0 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/iitis/PyQBench} \\
\hline
C3 & Code Ocean compute capsule & For example: 
$https://codeocean.com/2017/07/30/neurospeech-colon-an-open-source-software-for-parkinson-apos-s-speech-analysis/code$\\
\hline
C4 & Legal Code License & Apache License 2.0\\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, Qiskit, AWS Braket \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & 
\texttt{Python >= 3.8}\newline
\texttt{amazon-braket-sdk \textapprox= 1.33.0}\newline
\texttt{numpy \textapprox= 1.14.5}\newline
\texttt{scipy \textapprox= 1.7.3}\newline
\texttt{pandas \textapprox= 1.5.0}\newline
\texttt{pydantic \textapprox= 1.9.0}\newline
\texttt{qiskit \textapprox= 0.39.0}\newline
\texttt{mthree \textapprox= 1.1.0}\newline
\texttt{tqdm \textapprox= 4.64.1}\newline
\texttt{pyyaml \textapprox= 6.0}\\
\hline
C8 & If available Link to developer documentation/manual & For example: 
$http://mozart.github.io/documentation/$ \\
\hline
C9 & Support email for questions & \url{dexter2206@gmail.com}\\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

@@

The permanent link to code/repository or the zip archive should include the 
following requirements:

README.txt and LICENSE.txt.

Source code in a src/ directory, not the root of the repository.

Tag corresponding with the version of the software that is reviewed.

Documentation in the repository in a docs/ directory, and/or READMEs, as 
appropriate.

@@

Noisy intermediate-scale quantum
(NISQ)~\cite{preskill} devices are currently storming the market. We
have a selection of readily available quantum computers based on different
architectures. Historically, the first widely introduced quantum computing
architecture is D-Wave's quantum annealer~\cite{}.

https://quantumcomputingreport.com/scorecards/qubit-technology/

@@

@@

Set out the conclusion of this original software publication.

\section{Conflict of Interest}
Please select the appropriate text:

Potential conflict of interest exists:
We wish to draw the attention of the Editor to the following facts, which may 
be considered as potential conflicts of interest, and to significant financial 
contributions to this work. The nature of potential conflict of interest is 
described below: [Describe conflict of interest]

No conflict of interest exists:
We wish to confirm that there are no known conflicts of interest associated 
with this publication and there has been no significant financial support for 
this work that could have influenced its outcome.

@@

This work was supported by the Foundation for Polish Science (FNP) under grant
number POIR.04.04.00-00-17C1/18-00.

@@

\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and 
beyond." Quantum 2 (2018): 79.
\bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking 
gate-based quantum computers." Computer Physics Communications 220 (2017): 
44-55.
\bibitem{zhukov2019quantum} Zhukov, A. A., et al. "Quantum communication 
protocols as a benchmark for programmable quantum computers." Quantum 
Information Processing 18.1 (2019): 1-23.
\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu, 
and Raphael C. Pooser. "Generative model benchmarks for superconducting 
qubits." Physical Review A 99.6 (2019): 062323.
\bibitem{benedetti2018generative} Benedetti, Marcello, et al. "A generative 
modeling approach for benchmarking and training shallow quantum circuits." npj 
Quantum Information 5.1 (2019): 1-9.
\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for 
optimal single-shot discrimination of quantum measurements." Physical Review A 
98.4 (2018): 042103.
\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
\bibitem{nr} Lewandowska, Paulina and others. The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02. 
\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.
\end{thebibliography}

>>>>

@@

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this 
column} \\
\hline
C1 & Current code version & 0.1.0 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/iitis/PyQBench} \\
\hline
C3 & Code Ocean compute capsule & ?????????\\
\hline
C4 & Legal Code License & Apache License 2.0\\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, Qiskit, AWS Braket \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & 
\texttt{Python >= 3.8}\newline
\texttt{amazon-braket-sdk \textapprox= 1.33.0}\newline
\texttt{numpy \textapprox= 1.14.5}\newline
\texttt{scipy \textapprox= 1.7.3}\newline
\texttt{pandas \textapprox= 1.5.0}\newline
\texttt{pydantic \textapprox= 1.9.0}\newline
\texttt{qiskit \textapprox= 0.39.0}\newline
\texttt{mthree \textapprox= 1.1.0}\newline
\texttt{tqdm \textapprox= 4.64.1}\newline
\texttt{pyyaml \textapprox= 6.0}\\
\hline
C8 & If available Link to developer documentation/manual & ?????\\
\hline
C9 & Support email for questions & \url{dexter2206@gmail.com}\\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

@@

%The permanent link to code/repository or the zip archive should include the 
%following requirements: 
%
%README.txt and LICENSE.txt.
%
%Source code in a src/ directory, not the root of the repository.
%
%Tag corresponding with the version of the software that is reviewed.
%
%Documentation in the repository in a docs/ directory, and/or READMEs, as 
%appropriate.

@@

\todo[inline]{In particular, we compile circuits to standard gate sets of the vendor using compiler RECZNEGO?, and we perform experiments across different qubit subsets.}

quantum volume - '' has become the de-facto standard benchmark to quantify the capability of Noisy Intermediate-Scale Quantum (NISQ) devices '' \cite{pelofske2022volume}

Noisy intermediate-scale quantum
(NISQ)~\cite{preskill} devices are currently storming the market. We
have a selection of readily available quantum computers based on different
architectures. Historically, the first widely introduced quantum computing
architecture is D-Wave's quantum annealer.

@@

This software has two main contributions.

@@

In this study, we develop  a Python library PyQBench, an innovative open-source framework for benchmarking 
gate-based quantum computers.

%%%%%%%%%%%%%% 
PyQBench can benchmark NISQ devices by verifying their capability of
discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
measurements instead of predefined ones.
\section{Conflict of Interest}
No conflict of interest exists: We wish to confirm that there are no known
conflicts of interest associated with this publication and there has been no
significant financial support for this work that could have influenced its out-
come.

@@

This work is  supported by
the project “Near-term quantum computers Challenges, optimal implementations and applications” under Grant Number POIR.04.04.00-00-17C1/18-00, which is carried out within the Team-Net programme of the Foundation for Polish Science co-financed by the European Union under the European Regional Development Fund. 
PL is also a holder of European Union scholarship through the European Social Fund, 
grant InterPOWER (POWR.03.05.00-00-Z305).

@@

\bibitem{preskill} Preskill, John. "Quantum Computing in the NISQ era and 
beyond." Quantum 2 (2018): 79.
\bibitem{michielsen2017benchmarking} Michielsen, Kristel, et al. "Benchmarking 
gate-based quantum computers." Computer Physics Communications 220 (2017): 
44-55.
\bibitem{zhukov2019quantum} Zhukov, A. A., et al. "Quantum communication 
protocols as a benchmark for programmable quantum computers." Quantum 
Information Processing 18.1 (2019): 1-23.
\bibitem{hamilton2018generative} Hamilton, Kathleen E., Eugene F. Dumitrescu, 
and Raphael C. Pooser. "Generative model benchmarks for superconducting 
qubits." Physical Review A 99.6 (2019): 062323.
\bibitem{benedetti2018generative} Benedetti, Marcello, et al. "A generative 
modeling approach for benchmarking and training shallow quantum circuits." npj 
Quantum Information 5.1 (2019): 1-9.
\bibitem{puchala2018strategies} Puchała, Zbigniew, et al. "Strategies for 
optimal single-shot discrimination of quantum measurements." Physical Review A 
98.4 (2018): 042103.
\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.
\bibitem{watrous} Watrous, John (2018). The theory of quantum information. Cambridge university press.
\bibitem{nr} Lewandowska, Paulina and others. The web resource at \url{https://numericalshadow.org/}. Accessed on 2022-10-02. 
\bibitem{hausdorff} Hausdorff, Felix. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
\bibitem{toeplitz} Toeplitz, Otto. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.

\bibitem{pelofske2022volume} Pelofske, E., B{\"a}rtschi, A., Eidenbenz, S. (2022). Quantum volume in practice: What users can expect from NISQ devices. arXiv preprint arXiv:2203.03816.
\end{thebibliography}
